The Processing of American Indian/Alaska Native Children through non-Tribal

### 2019-12-30 ms.rmd
update natl files

```{r fctables.ncands}

@@

## $P(subst|inv)$

of all investigated, how many are ever substantiated?

from lifetables:

Because $P(inv|subst)=1$, and we've converted population incidence into annual age-adjusted probability, the ratio of events is the conditional probability

\[P(subst|inv) = \frac{d_{subst}}{d_{inv}}\]

make_conditionals<-function(num, denom){
  out<-num %>% 
  select(age, year, d) %>% 
  rename(d_num = d) %>% 
  left_join(denom %>% 
              select(age, year, d) %>% 
              rename(d_denom = d)) %>% 
  group_by(year) %>% 
  summarise(q = sum(d_num)/sum(d_denom))
  return(out)
}

sub_inv<-make_conditionals(subst_tables, investigation_tables)

@@

```{r fctables.pop}
fc_tables<-list()
years<-unique(afcars_fc$year)
race_ethn<-unique(afcars_fc$race_ethn)
index<-1
for(i in 1:5){
  for(j in 1:length(years)){
    for(r in 1:length(race_ethn)){
      temp<-afcars_fc %>% 
        filter(year==years[j])
      temp<-temp %>% 
        filter(race_ethn == race_ethn[r])
      temp<-temp %>% 
        filter(.imp==i)
      fc_tables[[index]]<-make_life_table(temp)
      index<-index+1
    }
  }
}
fc_tables<-bind_rows(fc_tables)

@@

```{r}
fc_post_inv_tables<-list()
years<-unique(afcars_fc_inv$year)
race_ethn<-unique(afcars_fc_inv$race_ethn)
index<-1
for(i in 1:5){
  for(j in 1:length(years)){
    for(r in 1:length(race_ethn)){
      temp<-afcars_fc_inv %>% 
        filter(year==years[j])
      temp<-temp %>% 
        filter(race_ethn == race_ethn[r])
      temp<-temp %>% 
        filter(.imp==i)
      fc_post_inv_tables[[index]]<-make_life_table(temp)
      index<-index+1
    }
  }
}
fc_post_inv_tables<-bind_rows(fc_post_inv_tables)

@@

@@

```{r}
fc_inv<-make_conditionals(fc_tables, investigation_tables)
fc_sub<-make_conditionals(fc_tables, subst_tables)
fc_ncands_inv<-make_conditionals(ncands_fc_tables, 
                                 investigation_tables)
fc_ncands_subst<-make_conditionals(ncands_fc_tables, 
                                 subst_tables)
```

>>>>

@@

@@

```{r fctables.pop}
fc_tables<-list()
years<-unique(afcars_fc$year)
race_ethn<-unique(afcars_fc$race_ethn)
index<-1
for(i in 1:length(afcars_fc$.imp)){
  for(j in 1:length(years)){
    for(r in 1:length(race_ethn)){
      temp<-afcars_fc %>% 
        filter(year==years[j])
      temp<-temp %>% 
        filter(race_ethn == race_ethn[r])
      temp<-temp %>% 
        filter(.imp==i)
      fc_tables[[index]]<-make_life_table(temp)
      index<-index+1
    }
  }
}
fc_tables<-bind_rows(fc_tables)

@@

```{r}
fc_post_inv_tables<-list()
years<-unique(afcars_fc_inv$year)
race_ethn<-unique(afcars_fc_inv$race_ethn)
index<-1
for(i in 1:length(afcars_fc_inv$.imp)){
  for(j in 1:length(years)){
    for(r in 1:length(race_ethn)){
      temp<-afcars_fc_inv %>% 
        filter(year==years[j])
      temp<-temp %>% 
        filter(race_ethn == race_ethn[r])
      temp<-temp %>% 
        filter(.imp==i)
      fc_post_inv_tables[[index]]<-make_life_table(temp)
      index<-index+1
    }
  }
}
fc_post_inv_tables<-bind_rows(fc_post_inv_tables)

@@

## p(tpr)

```{r}
tpr_tables<-list()
years<-unique(afcars_tpr$year)
race_ethn<-unique(afcars_tpr$race_ethn)
index<-1
for(i in 1:length(afcars_tpr$.imp)){
  for(j in 1:length(years)){
    for(r in 1:length(race_ethn)){
      temp<-afcars_tpr %>% 
        filter(year==years[j])
      temp<-temp %>% 
        filter(race_ethn == race_ethn[r])
      temp<-temp %>% 
        filter(.imp==i)
      tpr_tables[[index]]<-make_life_table(temp)
      index<-index+1
    }
  }
}
tpr_tables<-bind_rows(tpr_tables)

tpr_tables_c<-tpr_tables %>% 
  filter(age==17) %>% 
  group_by(year, race_ethn) %>% 
  summarise(c_mn = mean(c), cmax = max(c), cmin = min(c))

tpr_tables_c %>% 
  ggplot(aes(x=year, y = c_mn, 
             fill = race_ethn,
             group = race_ethn,
             ymin = cmin, ymax = cmax)) +
  geom_ribbon(alpha = .5) + 
  geom_line(aes(color = race_ethn)) + 
  xlab("Year") + 
  ylab("Proportion with parental rights terminated")
```

## P(sub|inv)

## p(sub|inv) = p(inv|sub) * p(sub) / p(inv) =
## p(sub) / p(inv)
ncands_sub_inv<-subst_tables %>% 
  mutate(sub_inv = q / investigation_tables$q)

ggplot(ncands_sub_inv %>% 
         filter(year==2016),
         aes(x = age, y = sub_inv, color = race_ethn)) + 
  geom_line()
```

@@

\[p(fc|inv) = \frac{p(fc, inv)}{p(inv)}\]

```{r}
fc_cond_inv<-fc_post_inv_tables %>% 
  mutate(fc_inv = q / investigation_tables$q)

ggplot(fc_cond_inv %>% 
         filter(year==2016),
         aes(x = age, y = fc_inv, color = race_ethn)) + 
  geom_line()
```

## P(FC|sub)
```{r}

fc_cond_sub<-fc_post_inv_tables %>% 
  mutate(fc_sub = q / subst_tables$q)

ggplot(fc_cond_sub %>% 
         filter(year==2016),
         aes(x = age, y = fc_sub, color = race_ethn)) + 
  geom_line()
```

## P(FC|tpr)
```{r}
### use bayes' rule because p(fc|tpr)=1
# \[P(B|A) = \frac{P(A|B)P(B)}{P(A)}\]
## P(tpr|fc) = p(fc|tpr)p(tpr) / p(fc)
## p(tpr|fc) = p(tpr)/p(fc)
fc_tpr_fc<-tpr_tables %>% 
  mutate(tpr_fc = q/ fc_tables$q)

ggplot(fc_tpr_fc %>% 
         filter(year==2016),
         aes(x = age, y = tpr_fc, color = race_ethn)) + 
  geom_line()
